DRAFT: Harmonisation and trait aggregation paper

### 2020-12-21 Paper/Results/SI.tex
21.12: Edits Summary and References

        \caption{Comparison of trait definitions between invertebrate trait databases. Only traits that are differently described across databases are listed. The definition is quoted if it enables differences to be identified, otherwise the differences are described. The hyphen indicates a missing trait. Reproduction was captured in multiple grouping features per database. Hence, differences for reproduction have been described in the paper. Body form traits are not different between databases, except that the North America (Vieira) database contains the trait Bluff (blocky) which does not appear in the other databases.}

@@

        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & \specialcell{North America \\ (Twardochleb)} & 
        North America (Vieira) & Australia & New Zealand \\

@@

\subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}

\subsubsection*{Comparison of the trait aggregation methods with each other}
\label{sec:compa_aggr_methods}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
    \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets. Displayed are means of absolute differences in trait affinities with standard deviations (truncated at 0). Compared aggregation methods are displayed on the y-axis. N indicates the number of cases where differences occurred. Total number of cases: Australia 2223, Europe 3352, New Zealand 777, and North America 4080.}
    \label{fig:comp_aggr_methods}
\end{figure}

>>>>

        \caption{Comparison of trait definitions between invertebrate trait databases. Only traits that are differently described across databases are listed. The definition is quoted if it enables differences to be identified, otherwise the differences are described. The hyphen indicates a missing trait. Reproduction was captured in multiple grouping features per database. Hence, differences for reproduction have been described in the paper. Body form traits are not different between databases, except that the North America (Vieira et al.) database contains the trait Bluff (blocky) which does not appear in the other databases.}

@@

        Trait & \specialcell{Freshwater- \\ ecology.info} & Tachet & \specialcell{North America \\ (Twardochleb et al.)} & 
        North America (Vieira et al.) & Australia & New Zealand \\

@@

% \subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}

% \subsubsection*{Comparison of the trait aggregation methods with each other}
% \label{sec:compa_aggr_methods}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=16.5cm, height=10cm]{Comparison_trait_agg_methods.png}
%     \caption{Comparison of trait aggregation methods when aggregating over all traits for all datasets. Displayed are means of absolute differences in trait affinities with standard deviations (truncated at 0). Compared aggregation methods are displayed on the y-axis. N indicates the number of cases where differences occurred. Total number of cases: Australia 2223, Europe 3352, New Zealand 777, and North America 4080.}
%     \label{fig:comp_aggr_methods}
% \end{figure}
